### 2021-02-24 paper.Rmd
small tweaks to intro

The area of visualising high-dimensions is very large, so the focus of this review will be on linear projections, in particular as provided by the grand tour [@Asimov1985-xr; @Buja2005-cx]. An overview of the technique, and recent developments is provided, along with how these techniques can be used in a variety of applications, and to help understand nonlinear dimension reduction results.

>>>>

The focus of this review will be on linear projections, in particular, as provided by the grand tour [@Asimov1985-xr; @Buja2005-cx]. The reason being that it is not feasible to adequately the very large area of visualising high-dimensions, and there have been numerous developments in tours recently.  An overview of the technique, and new modifications is provided, along with how these techniques can be used in a variety of applications, and to help understand nonlinear dimension reduction results.
